---
title: "Tidysynth Practical for Synthetic Controls Tutorial"
author: "Victor Yu"
date: "06/04/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```

Load the dataset, which should be in the folder you downloaded from the github repository at  https://github.com/VictorNautica/synthetic_controls.

```{r load}
data <- readRDS("~/projects/SC tutorial/practical_df.Rds")
```


## 1) Exploratory Analysis of the Dataset

1.1) How many local authorities are in the East of England?

```{r 1.1}
length(unique(data$local_authority))
```

There are 45 local authorities.

1.2) What local authority has the lowest obesity rate in 2020?

```{r 1.2}
data %>% filter(timeperiod == 2020) %>% filter(percentage_of_adults_aged_18_classified_as_overweight_or_obese == min(percentage_of_adults_aged_18_classified_as_overweight_or_obese)) %>% pull(local_authority)
```

Mid Suffolk at 51.1%.

1.3) Which local authority(ies), in which year had the absolute lowest adult overweight+obesity rate in the dataset, and what was its value?

```{r 1.3}
data %>% filter(percentage_of_adults_aged_18_classified_as_overweight_or_obese == max(percentage_of_adults_aged_18_classified_as_overweight_or_obese)) %>% select(local_authority, timeperiod, percentage_of_adults_aged_18_classified_as_overweight_or_obese)
```

Norwich and Thurrock in 2009, 2018 respectively at 75.9%.

1.4) Which local authority, in which year had the absolute lowest adult overweight+obesity rate in the dataset, and what was its value?

```{r 1.4}
data %>% filter(percentage_of_adults_aged_18_classified_as_overweight_or_obese == min(percentage_of_adults_aged_18_classified_as_overweight_or_obese)) %>% select(local_authority, timeperiod, percentage_of_adults_aged_18_classified_as_overweight_or_obese)
```

Fenland local authority in 2025, with 37%.

2) What time periods are covered in the dataset?

```{r 2}
data$timeperiod %>% unique()
```

Annual time-series data from 2006 to 2025.

3) Explore the variables in the dataset. Why might you think these variables are included?

```{r 3}
data %>% colnames()
```

These variables would be highly related to after effects from the intervention.

## 2) Tidysynth

4) Install the tidysynth package if you haven't already, and load it in.

```{r prep tidysynth}
# install.packages("tidysynth")
library("tidysynth")
```

5) Initialise the synthetic control object with `synthetic_control()`.

```{r initialise}
sc_initialise <-
  data %>% synthetic_control(
    outcome = percentage_of_adults_aged_18_classified_as_overweight_or_obese, 
    unit = local_authority,
    time = timeperiod,
    i_unit = "Fenland",
    i_time = 2020,
    generate_placebos = T
  )
```

Remember, you won't be able to view the `sc_initialise` object in the standard R viewer. You'll have to call it in the console.

5.1) Generate aggregate predictors

We want to use the entire pre-intervention time period to create aggregate predictors. The standard method is to just take the mean value. However, these is one variable where we can just take one value (doing the mean on this variable would just return the same value and be pointless), which variable is it?

```{r agg_predictors}
sc_predictors <- sc_initialise %>% generate_predictor(
  time_window = 2006:2020,
  utilisation_of_outdoor_space_for_exercise_health_reasons = mean(utilisation_of_outdoor_space_for_exercise_health_reasons),
  percentage_of_physically_active_adults = mean(percentage_of_physically_active_adults),
  percentage_of_physically_inactive_adults = mean(percentage_of_physically_inactive_adults),
  percentage_of_adults_walking_for_travel_at_least_three_days_per_week = mean(
    percentage_of_adults_walking_for_travel_at_least_three_days_per_week
  ),
  percentage_of_adults_cycling_for_travel_at_least_three_days_per_week = mean(
    percentage_of_adults_cycling_for_travel_at_least_three_days_per_week
  ),
  proportion_of_the_population_meeting_the_recommended_5_a_day_on_a_usual_day_adults = mean(proportion_of_the_population_meeting_the_recommended_5_a_day_on_a_usual_day_adults),
  proportion_of_the_population_with_gym_membership = mean(proportion_of_the_population_with_gym_membership)
) %>% 
  generate_predictor(time_window = 2020,
                     imd_2015 = deprivation_score_imd_2015)
```

5.2) Generate weights

```{r generate_weights}
sc_weights <- sc_predictors %>% generate_weights(
    optimization_window = 2006:2020,
    margin_ipop = .02,
    sigf_ipop = 7,
    bound_ipop = 6
  )
```

5.3) Generate SC

```{r generate_sc}
sc_full <- generate_control(sc_weights)
```

5.4) What local authorities make up the synthetic counterpart for Fenland (>0.1)?

```{r grab weights}
sc_full %>% grab_unit_weights() %>% arrange(-weight)
```
Huntingdonshire, Thurrock, and Epping Forest.


5.5) What predictor variables don't make up more than 0.1 of the weighted component of Fenland's synthetic counterpart?

```{r grab_predictor}
sc_full %>% grab_predictor_weights() %>% arrange(-weight)
```


5.6) Try plotting the placebos with both prune set to T and F, do you notice something? What does this mean?

```{r placebo prune plot}
sc_full %>% plot_placebos(prune = TRUE)
sc_full %>% plot_placebos(prune = FALSE)
```

It means that no placebo controls had a MSPE 2x beyond Fenland's pre-intervention period.

5.7) Lastly, grab the significances from Fisher's exact p value. What is Fenland's MSPE Ratio? Do any other local authorities have a p-value <0.05?

```{r grab function}
sc_full %>% grab_signficance()
```

Fenland has an MSPE ratio of 15.4, and Huntingdonshire also has a statistically significant p_value.