---
title: "Tidysynth Practical for Synthetic Controls Tutorial"
author: "Victor Yu"
date: "06/04/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```

Load the dataset, which should be in the folder you downloaded from the github repository at  https://github.com/VictorNautica/synthetic_controls.

```{r load}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
data <- readRDS("practical_df.Rds")
```


## 1) Exploratory Analysis of the Dataset

1.1) How many local authorities are in the East of England?

```{r 1.1}
```

ANSWER:

1.2) What local authority has the lowest obesity rate in 2020?

```{r 1.2}
```

ANSWER:

1.3) Which local authority(ies), in which year had the absolute lowest adult overweight+obesity rate in the dataset, and what was its value?

```{r 1.3}
```

ANSWER:

1.4) Which local authority, in which year had the absolute lowest adult overweight+obesity rate in the dataset, and what was its value?

```{r 1.4}
```

ANSWER:

2) What time periods are covered in the dataset?

```{r 2}
```

ANSWER:

3) Explore the variables in the dataset. Why might you think these variables are included?

```{r 3}
```

ANSWER:

## 2) Tidysynth

4) Install the tidysynth package if you haven't already, and load it in.

```{r prep tidysynth}
# install.packages("tidysynth")
library("tidysynth")
```

5) Initialise the synthetic control object with `synthetic_control()`.

```{r initialise}
sc_initialise <-
  data %>% synthetic_control(
    outcome = percentage_of_adults_aged_18_classified_as_overweight_or_obese, 
    unit = local_authority,
    time = timeperiod,
    i_unit = "Fenland",
    i_time = 2020,
    generate_placebos = T
  )
```

Remember, you won't be able to view the `sc_initialise` object in the standard R viewer. You'll have to call it in the console.

5.1) Generate aggregate predictors

We want to use the entire pre-intervention time period to create aggregate predictors. The standard method is to just take the mean value. However, these is one variable where we can just take one value (doing the mean on this variable would just return the same value and be pointless), which variable is it?

```{r agg_predictors}
sc_predictors <- ? %>% 
  generate_predictor(
  time_window = 2006:2020,
  utilisation_of_outdoor_space_for_exercise_health_reasons = mean(),
  percentage_of_physically_active_adults = ,
  percentage_of_physically_inactive_adults = ,
  percentage_of_adults_walking_for_travel_at_least_three_days_per_week = ,
  percentage_of_adults_cycling_for_travel_at_least_three_days_per_week = ,
  proportion_of_the_population_meeting_the_recommended_5_a_day_on_a_usual_day_adults = ,
  proportion_of_the_population_with_gym_membership = 
) %>% 
  generate_predictor(time_window = 2020,
                     ? = ?)
```

ANSWER:

5.2) Generate weights

```{r generate_weights}
sc_weights <- ? %>% generate_weights(
    optimization_window = 2006:2020,
    margin_ipop = .02,
    sigf_ipop = 7,
    bound_ipop = 6
  )
```

5.3) Generate the SC

```{r generate_sc}
sc_full <- generate_control()
```

5.4) What local authorities make up the synthetic counterpart for Fenland (>0.1)?

```{r grab weights}
sc_full
```

ANSWER:

5.5) What predictor variables don't make up more than 0.1 of the weighted component of Fenland's synthetic counterpart?

```{r grab_predictor}
sc_full %>%
```

ANSWER:

5.6) Try plotting the placebos with both prune set to T and F, do you notice something? What does this mean?

```{r placebo prune plot}
sc_full %>% 
sc_full %>% 
```

ANSWER:

5.7) Lastly, grab the significances from Fisher's exact p value. What is Fenland's MSPE Ratio? Do any other local authorities have a p-value <0.05?

```{r grab function}
sc_full %>% 
```

ANSWER: